\Large Exponential Random Graph Models with Big Networks: Maximum Pseudolikelihood Estimation and the\\Parametric Bootstrap

### 2017-06-25 TeX/paper.tex
cosponsorship description

In order to demonstrate the computational advantage of the bootstrapped MPLE to the commonly used MCMLE we apply both approaches to the data on Cosponsorships in the U.S. Senate and U.S. House of Representatives for the 93rd to 108th Congresses developed by Fowler (2006) \cite{Fowler2006a} \cite{Fowler2006b}. The cosponsorship network consists of 2635 nodes and contains information of over 280,000 pieces of legislation proposed in the U.S. House and Senate for the time period 1973 - 2004. In this network each node indicates on cosponsor and an edge indicates the link of each cosponsor of a piece of legislation to its sponsor. The endogenous statistics we include into this model are the number of edges and the alternating k-star statistic as it was introduced by Snijders et al. \cite{SnijdersTomA.B..2006} and modified by Hunter and Handcock (2006) \cite{Hunter.2006}. The alternating k-star statistic adds one network statistic to the model equal to a weighted alternating sequence of k-star statistics with weight parameter $\lambda$ and is a way to include a networks entire degree distribution as a network statistic. In this model we fix the weight paramter $\lambda=0.4975$. 

@@

The two nodal attributes we consider for this network are the year the majority opinion was drafted as well as an attribute that indicates whether a case appears on the Oxford list of salient cases. In order to include nodal covariates into the ERGM, the vector of nodal attributes is expanded into an artificial matrix $C$, which has the same dimensions as $G$. The first row of matrix $C$ consists of the first actor's attribute, repeated $N$ times. The second row of matrix $C$, consists of the second actor's attribute, repeated $N$ times, and so on. Then, the statistics for a nodal covariate is defined as

>>>>

In order to demonstrate the computational advantage of the bootstrapped MPLE to the commonly used MCMLE we apply both approaches to the data on Cosponsorships in the U.S. Senate and U.S. House of Representatives for the 93rd to 108th Congresses developed by Fowler (2006) \cite{Fowler2006a} \cite{Fowler2006b}. The cosponsorship network consists of 2635 nodes and contains information of over 280,000 pieces of legislation proposed in the U.S. House and Senate for the time period 1973 - 2004. In this network bills are tied together based on the similarity of the sets of legislators who cosponsor them. The endogenous statistics we include into this model are the number of edges and the alternating k-star statistic as it was introduced by Snijders et al. \cite{SnijdersTomA.B..2006} and modified by Hunter and Handcock (2006) \cite{Hunter.2006}. The alternating k-star statistic adds one network statistic to the model equal to a weighted alternating sequence of k-star statistics with weight parameter $\lambda$ and is a way to include a networks entire degree distribution as a network statistic. In this model we fix the weight paramter $\lambda=0.4975$. 

@@

The nodal attribute that we implement for this network 
 In order to include nodal covariates into the ERGM, the vector of nodal attributes is expanded into an artificial matrix $C$, which has the same dimensions as $G$. The first row of matrix $C$ consists of the first actor's attribute, repeated $N$ times. The second row of matrix $C$, consists of the second actor's attribute, repeated $N$ times, and so on. Then, the statistics for a nodal covariate is defined as
